Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex
Updates from Overleaf
caption for MR relation

\section{Introduction}
\DL{please igonre Fig 7 for now. Labels/markers in the AlphaVir plots in Fig 5,6 will be updated based on Jens Kauffman's comments} 
The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes). Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times. Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.

@@

\begin{figure*}
\centering
\includegraphics[trim=20 20 0 0, clip, width=1.1\textwidth]{\figpath/3by2_clumpProp_allss.png}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
\label{fig:alpha16-28}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. The colored lines show the loci expected for various visual extinctions ($A_V$), which corresponds to lines of constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. \AP{please implement the following} The reference lines with different $A_V$ are computed from \Eq{constantcolumndensity}.
\DL{Ignore the blue dotted line for now.}
\label{fig:MR}}
\end{figure*}

>>>>

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle --- galaxies accrete gas from the intergalactic medium (IGM) to fuel \SF (and feed their supermassive black holes). Subsequent feedback replenishes and enriches the circumgalactic medium with part of this material. The general consensus is that the growth of \highz galaxies are triggered and supported by massive gas inflows from mergers and/or cosmic web at early cosmic times. Back then, galaxies themselves are more gas-rich and their molecular fraction possibly higher compared to present-day galaxies.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=1.05\textwidth]{\figpath/3by2_clumpProp_allss}
\caption{Same as \Fig{larsons_single}, except star symbols are showing MCs identified across all evolutionary stages traced in our simulation, which are color-coded by the SFR of \flower in those stages. Left panels show MCs identified using a low $n_{\rm cut}$\eq0.53\,\cc and right panels show MCs identified using a high $n_{\rm cut}$\eq19\,\cc.
\label{fig:alpha16-28}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
\label{fig:MR}}
\end{figure*}
